## % FIT10 data

Percentage of colonoscopies with a FIT10+ result

```{r}
#| echo: false

library(dplyr)
library(kableExtra)

# Call subscript
source("C:/Users/martin.bloyce/OneDrive - NHS England/Documents/GitHub/diagnostics_endoscopy_stocktake/endoscopy_fit.R")

# Create table visual output
kable(fit_table,
             col.names = colnames(fit_table),
             caption = "Sample Table") %>%
               kable_styling(full_width = FALSE) %>%
                add_header_above(c(" ", "Percentage of colonoscopies with a FIT10+ result" = 8)) %>%
               row_spec(0, bold = TRUE, color = "white", background = "gray") %>%
               column_spec(9, color = "white",
              background = spec_color(fit_table$percentageFit10[1:12], begin = 0.9, end = 0.4, option = 'H'))

# Visualise charts
a
b

```

## Endoscopy activity

DM01 activity used, for gastroscopies and colonoscopies only.

```{r}
#| echo: false

library(dplyr)
library(kableExtra)

# Call subscript
source("C:/Users/martin.bloyce/OneDrive - NHS England/Documents/GitHub/diagnostics_endoscopy_stocktake/endoscopy_activity.R")

# Create table visual output
kable(master,
             col.names = colnames(master),
             caption = "Sample Table") %>%
               kable_styling(full_width = FALSE) %>%
                add_header_above(c(" ", "DM01 diagnostic activity (gastroscopies and colonoscopies only)" = 3)) %>%
               row_spec(0, bold = TRUE, color = "white", background = "gray") %>%
               column_spec(4, color = "black",
                background = ifelse(master$percent_of_baseline >= 100, "green", ifelse(master$percent_of_baseline > 90, "yellow", "red")))


```

## Future demand

Lists per week used for current position, with following models used for future demand predictions: - 120% activity - Current demand, plus 5% uplift for each subsequent year (as specified in the Richards' Review)

```{r}
#| echo: false

library(dplyr)
library(kableExtra)

# Call subscript
source("C:/Users/martin.bloyce/OneDrive - NHS England/Documents/GitHub/diagnostics_endoscopy_stocktake/future_demand_modelling.R")

# Create table visual output
kable(lists_per_week,
             col.names = colnames(lists_per_week),
             caption = "Sample Table") %>%
               kable_styling(full_width = FALSE) %>%
                add_header_above(c(" ", "Lists per week" = 6)) %>%
               row_spec(0, bold = TRUE, color = "white", background = "gray") %>%
               column_spec(4, background = lists_per_week$gradient_colour)

```

## Lists

List types used by unit:

```{r}
#| echo: false

library(dplyr)
library(kableExtra)

# Call subscript
source("C:/Users/martin.bloyce/OneDrive - NHS England/Documents/GitHub/diagnostics_endoscopy_stocktake/endoscopy_lists.R")

lists_chart

```
